\subsection{ISA}
\label{sec:isa}
As stated previously, our MIPS implementation runs a subset of the 
MIPS instruction set. All instructions required by the execise have 
been implemented and tested. 

In MIPS all instructions have the same width, 32 bits, and can be 
categorized into three categories R-, I- and J-type instructions. 
The bit layout of each of the instruction types is given in the 
figures \ref{fig:rtype_format}, \ref{fig:itype_format} and 
\ref{fig:jtype_format}. The subset of instructions our processor 
supports falls within all of the three categories. 

\FloatBarrier
\subsubsection{R-Type instructions}
R-type instructions have a total of three register fields, as well as 
a function and shift field. Following this, R-Type instruction coding 
is used for ALU operations as they have one destination and two source 
registers. The R-Type instructions our implementation supports are shown
in table~\ref{table:rtype_instructions}.

\input{figures/isa/r_type}
\begin{table}[h]
    \begin{tabular}{l|l|l|l}
    Phonetic & Operation & Opcode & Function \\

    \hline
    ADD \$rd, \$rs, \$rt & \$rd = \$rs + \$rd   & 000000 & 100000 \\
    SUB \$rd, \$rs, \$rt & \$rd = \$rs - \$rd   & 000000 & 100011 \\ 
    AND \$rd, \$rs, \$rt & \$rd = \$rs and \$rd & 000000 & 100100 \\ 
    OR  \$rd, \$rs, \$rt & \$rd = \$rs or \$rd  & 000000 & 100101 \\  
    SLT \$rd, \$rs, \$rt & if \$rs $<$ \$rt \$rd = 1 else \$rd = 0  & 000000 & 101010 \\
    \hline
    \end{tabular}

    \caption{Supported R-Type instructions}
    \label{table:rtype_instructions}
\end{table}

\FloatBarrier
\subsubsection{I-Type instructions}
I-Type instructions have half of the instruction word reserved for an 
immediate value, and hence only have room for two register designators. 
This encoding type is therefore used to map instructions that use immediate
values, such as load immediate as well as load and store word. 
The I-Type instructions our implementation supports are shown in 
table~\ref{table:itype_instructions}.


\input{figures/isa/i_type}
\begin{table}[h]
    \begin{tabular}{l|l|l|l}

    Phonetic & Operation & Opcode \\
    \hline
    BEQ \$rs, \$rt, imm  & if \$rs == \$rt \$PC += 1 + imm & 000100 \\
    LUI \$rs, imm        & \$rs = imm $<<$ 16                & 001111 \\
    SW \$rt, imm(\$rs)   & mem[\$rs+imm] = \$rt            & 101011 \\
    LW \$rt, imm(\$rs)   & \$rt = mem[\$rs+imm]            & 100011 \\
    \hline
    
    \end{tabular}

    \caption{Supported I-Type instructions}
    \label{table:itype_instructions}
\end{table}

\FloatBarrier
\subsubsection{J-Type instructions}
J-Type instructions have an even larger immediate field with a width 
of 26 bits. This encoding is mainly used to encode various jump instructions.
The J-Type instruction our implementation supports is shown in 
table~\ref{table:jtype_instructions}.

\input{figures/isa/j_type}
\begin{table}[h]
    \begin{tabular}{l|l|l|l}

    Phonetic & Operation & Opcode \\
    \hline
    J imm  & \$PC = (PC \& 0xf0000000) | (imm $<<$ 2) & 000010 \\
    \hline
    
    \end{tabular}

    \caption{Supported J-Type instructions}
    \label{table:jtype_instructions}
\end{table}
